\vspace{-0.30in} \Large \bf \editchange{Snowball}: The Power of Metastable Consensus

### 2020-11-03 figures/analysis2.tex
add initial source and 'fr' make target

\usetikzlibrary{decorations.pathreplacing}
\begin{tikzpicture}[x=1.12cm, scale=0.8, every node/.append style={transform shape}]
    \draw[line width=0.2ex, line cap=round] (0,0) -- (7,0); %edit here for the axis
    \foreach \x in {0,1,3,5,7} % edit here for the vertical lines
    \draw[line width=0.2ex, line cap=round, shift={(\x,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
    \foreach \x in {0.5,1.5} % edit here for the vertical lines
    \draw[line width=0.15ex, line cap=round, shift={(\x,0)},color=black] (0pt,2pt) -- (0pt,-2pt);
    \foreach \x/\y/\z in {
        0/$s_{c/2}$/a,
        1/$s_{ps}$/b,
        3/$s_{c/2+\Delta}$/c,
        5/$s_c$/d,
        7/$s_n$/e}
    \draw[line width=0.2ex, shift={(\x,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below] (\z) {\y};
    \foreach \x/\y/\z in {
        0.5/\small$s_{ps-1}$/f,
        1//h,
        1.5/\small$s_{ps+1}$/g}
    \draw[line width=0.2ex, shift={(\x,0)},color=black] (0pt,0pt) -- (0pt,2pt) node[above] (\z) {\y};

    \begin{scope}[line width=0.15ex]
        %\path[->] (c) edge[out=-90, in=-85, looseness=0.7] node[above] {} (d);
        \path[->] (c) edge[out=-90, in=-90, looseness=0.7] node[above] {$\epsilon$} (b);
        \path[->] (h) edge[out=90, in=90, looseness=2] node[above,xshift=-0.5in] {\small$P(s_{ps} \to s_{ps-1})$} (f);
        \path[->] (h) edge[out=90, in=90, looseness=2] node[above,xshift=+0.4in] {\small$P(s_{ps} \to s_{ps+1})$} (g);
    \end{scope}
    %\draw [thick,decoration={brace,raise=1ex, amplitude=2ex},decorate] (5, 0) -- (7, 0) node[midway,above,yshift=3.5ex] {$b$};
\end{tikzpicture}

>>>>

\usetikzlibrary{decorations.pathreplacing}
\begin{tikzpicture}[x=1.12cm, scale=0.8, every node/.append style={transform shape}]
    \draw[line width=0.2ex, line cap=round] (0,0) -- (8,0); %edit here for the axis
    \foreach \x in {0,4,6.5,8} % edit here for the vertical lines
    \draw[line width=0.2ex, line cap=round, shift={(\x,0)},color=black] (0pt,3pt) -- (0pt,-3pt);
    \foreach \x/\y/\z in {%
        0/$0$/a,
        4/${c/2}$/b,
        6.5/$$/c,
        8/$c$/d}
    \draw[line width=0.2ex, shift={(\x,0)},color=black] (0pt,0pt) -- (0pt,-3pt) node[below] (\z) {\y};

    \begin{scope}[line width=0.15ex]
        \path[->] (c) edge[out=-90, in=-90, looseness=0.4] node[above] {$\le \varepsilon$} (a);
    \end{scope}
    \draw [thick,decoration={brace,raise=1ex, amplitude=2ex},decorate] (4, 0) -- (6.5, 0) node[midway,above,yshift=3.5ex] {$\delta$};
\end{tikzpicture}

### 2020-11-03 figures/cash-system-b.tex
add initial source and 'fr' make target

\definecolor{lightgray}{HTML}{dddddd}
\definecolor{medgray}{HTML}{cccccc}
\definecolor{medgray2}{HTML}{bbbbbb}
\definecolor{darkgray}{HTML}{aaaaaa}
\definecolor{lightgp}{HTML}{ddddee}
\begin{tikzpicture}[x=1.12cm, scale=0.7, every node/.append style={transform shape}]
    \begin{scope}[all/.style={draw,fill=white,minimum height=0.5cm, minimum width=0.5cm},line width=0.08ex]

        \node[all, label={[anchor=east]left:$\texttt{TX}_g$},
        rectangle,minimum width=0.5in, minimum height=0.4in, line width=0.1ex] (a0) at (0, 0) {};
        \node[all, label={[anchor=east]left:$\texttt{TX}_a$}, rectangle,minimum width=1in, minimum height=0.55in, line width=0.1ex]
        (a1) at (-1.45, -2) {};
        \node[all, label={[anchor=west]right:$\texttt{TX}_b$}, rectangle,minimum width=1in, minimum height=0.55in, line width=0.1ex]
        (a2) at (1.45, -2) {};
        \node[all, label={[anchor=east]left:$\texttt{TX}_c$}, rectangle,minimum width=1in, minimum height=0.55in, line width=0.1ex]
        (a3) at (-1.45, -4) {};

@@

@@

        \begin{scope}[line width=0.15ex]
        \path[->] (a1) edge[out=90, in=-110] node[sloped,above] {} (a0) ;
        \path[->] (a2) edge[out=100, in=-70] node[sloped,above] {} (a0) ;
        \path[->] (a3) edge[out=100, in=-90] node[sloped,above] {} (a1) ;
        \end{scope}
        %\node[] (p1) at (3, 0.5) {\footnotesize$\mathcal{P}_{T_1}$};
        %\node[] (p2) at (3, 0) {\footnotesize$\mathcal{P}_{T_2} = \mathcal{P}_{T_3}$};
        %\node[] (p3) at (3, -0.5) {\footnotesize$\mathcal{P}_{T_9} = \mathcal{P}_{T_6} = \mathcal{P}_{T_7}$};
        \begin{scope}[color=darkgray,dashed,line width=0.2ex]
        %\path[->] (p1) edge[out=180, in=0] node[sloped,above] {} (pt1) ;
        %\path[->] (p2) edge[out=180, in=60] node[sloped,above] {} (pt2) ;
        %\path[->] (p3) edge[out=-90, in=30] node[sloped,above] {} (pt3) ;
        \end{scope}
    \end{scope}
\end{tikzpicture}

>>>>

\definecolor{lightgray}{HTML}{dddddd}
\definecolor{medgray}{HTML}{cccccc}
\definecolor{medgray2}{HTML}{bbbbbb}
\definecolor{darkgray}{HTML}{999999}
\definecolor{lightgp}{HTML}{ddddee}
\begin{tikzpicture}[x=1.12cm, scale=0.7, every node/.append style={transform shape}]
    \begin{scope}[all/.style={draw,fill=white,minimum height=0.5cm, minimum width=0.5cm},line width=0.08ex]
    \begin{scope}[color=darkgray,dashed,line width=0.2ex]
        \node[all, label={[anchor=east, font=\fontsize{14}{14}]left:$\texttt{TX}_g$},
        rectangle,minimum width=0.5in, minimum height=0.4in, line width=0.15ex] (a0) at (0, 0) {};
        \node[all, label={[anchor=east, font=\fontsize{14}{14}]left:$\texttt{TX}_a$}, rectangle,minimum width=1in, minimum height=0.55in, line width=0.15ex]
        (a1) at (-1.45, -2) {};
        \node[all, label={[anchor=west, font=\fontsize{14}{14}]right:$\texttt{TX}_b$}, rectangle,minimum width=1in, minimum height=0.55in, line width=0.15ex]
        (a2) at (1.45, -2) {};
        \node[all, label={[anchor=east, font=\fontsize{14}{14}]left:$\texttt{TX}_c$}, rectangle,minimum width=1in, minimum height=0.55in, line width=0.15ex]
        (a3) at (-1.45, -4) {};
    \end{scope}

@@

        \node[rectangle, fill=lightgray, draw, minimum width=1ex](ain) at (-1.45, -1.5) {};
        \node[rectangle, fill=lightgray, draw, minimum width=1ex](bin) at (1.45, -1.5) {};
        \node[rectangle, fill=lightgray, draw, minimum width=1ex](aout) at (-1.45, -2.5) {};
        \node[rectangle, fill=lightgray, draw, minimum width=1ex](cin) at (-1.45, -3.5) {};
        \node[rectangle, fill=lightgray, draw, minimum width=1ex](gout) at (0, -0.3) {};

@@

        \begin{scope}[line width=0.15ex]
        \path[->] (ain) edge[out=90, in=-110] node[sloped,above] {} (gout) ;
        \path[->] (bin) edge[out=100, in=-70] node[sloped,above] {} (gout) ;
        \path[->] (cin) edge[out=100, in=-90] node[sloped,above] {} (aout) ;
        \path[->] (b1) edge[out=100, in=180] node[sloped,above] {} (ain);
        \path[->] (b2) edge[out=100, in=0] node[sloped,above] {} (ain);
        \path[->] (b3) edge[out=100, in=180] node[sloped,above] {} (bin);
        \path[->] (b4) edge[out=100, in=0] node[sloped,above] {} (bin);
        \path[->] (b5) edge[out=100, in=180] node[sloped,above] {} (cin);
        \path[->] (b6) edge[out=100, in=0] node[sloped,above] {} (cin);
        \path[->] (aout) edge[out=180, in=-90, looseness=1.3] node[sloped,above] {} (b1);
        \path[->] (aout) edge[out=0, in=-90, looseness=1.3] node[sloped,above] {} (b2);
        \end{scope}
        %\node[] (p1) at (3, 0.5) {\footnotesize$\mathcal{P}_{T_1}$};
        %\node[] (p2) at (3, 0) {\footnotesize$\mathcal{P}_{T_2} = \mathcal{P}_{T_3}$};
        %\node[] (p3) at (3, -0.5) {\footnotesize$\mathcal{P}_{T_9} = \mathcal{P}_{T_6} = \mathcal{P}_{T_7}$};
        \begin{scope}[color=darkgray,dashed,line width=0.2ex]
        %\path[->] (p1) edge[out=180, in=0] node[sloped,above] {} (pt1) ;
        %\path[->] (p2) edge[out=180, in=60] node[sloped,above] {} (pt2) ;
        %\path[->] (p3) edge[out=-90, in=30] node[sloped,above] {} (pt3) ;
        \end{scope}
    \end{scope}
\end{tikzpicture}

### 2020-11-03 figures/dag-conflict-set.tex
add initial source and 'fr' make target

\definecolor{lightgray}{HTML}{dddddd}
\definecolor{medgray}{HTML}{cccccc}
\definecolor{medgray2}{HTML}{bbbbbb}
\definecolor{darkgray}{HTML}{aaaaaa}
\definecolor{lightgp}{HTML}{ddddee}
\begin{tikzpicture}[x=1.12cm, scale=0.9, every node/.append style={transform shape}]
    \begin{scope}[all/.style={draw, minimum height=0.5cm, minimum width=0.5cm},line width=0.08ex]
        \node[fill=lightgp, circle,minimum width=1cm] (pt1) at (0, 0) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt4) at (-1.5, -2) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt5) at (-0.5, -2) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt6) at (-2, -3) {};
        \fill[color=lightgp] plot[smooth cycle] coordinates { (1.2, -1) (0.9, -1.4) (-0.9, -1.4) (-1.2, -1) (-0.9, -0.6) (0.9, -0.6)} node (pt2) {};
        \fill[color=lightgp] plot[smooth cycle] coordinates {(2.1, -1.75) (2, -2.4) (0.6, -3.4) (0, -3.5) (-0.3, -3.3)(-0.3, -2.8) (0.1, -2.4) (1.2, -1.65) (1.7, -1.5) } node (pt3) {};
        \node[all, draw,fill=darkgray] (b0) at (0, 0) {$T_1$};
        \node[all, draw,fill=darkgray] (b1) at (-0.8, -1) {$T_2$};
        \node[all, draw,fill=white] (b2) at (0.8, -1) {$T_3$};
        \node[all, draw,fill=medgray] (b3) at (-1.5, -2) {$T_4$};
        \node[all, draw,fill=medgray2] (b4) at (-0.5, -2) {$T_5$};
        \node[all, draw,fill=white] (b5) at (0.9, -2.5) {$T_6$};
        \node[all, draw,fill=white] (b6) at (1.7, -2) {$T_7$};
        \node[all, draw,fill=lightgray] (b7) at (-2, -3) {$T_8$};
        \node[all, draw,fill=lightgray] (b8) at (0.2, -3) {$T_9$};
        \begin{scope}[line width=0.2ex]
        \path[->] (b1) edge[out=90, in=-110] node[sloped,above] {} (b0) ;
        \path[->] (b2) edge[out=100, in=-70] node[sloped,above] {} (b0) ;
        \path[->] (b3) edge[out=90, in=-110] node[sloped,above] {} (b1) ;
        \path[->] (b4) edge[out=90, in=-70] node[sloped,above] {} (b1) ;
        \path[->] (b5) edge[out=100, in=-110] node[sloped,above] {} (b2) ;
        \path[->] (b6) edge[out=120, in=-70] node[sloped,above] {} (b2) ;
        \path[->] (b7) edge[out=90, in=-90] node[sloped,above] {} (b3) ;
        \path[->] (b7) edge[out=0, in=-110] node[sloped,above] {} (b4) ;
        \path[->] (b8) edge[out=90, in=-70] node[sloped,above] {} (b4) ;
        \end{scope}
        \node[] (p1) at (3, 0.5) {\footnotesize$\mathcal{P}_{T_1}$} ;
        \node[] (p2) at (3, 0) {\footnotesize$\mathcal{P}_{T_2} = \mathcal{P}_{T_3}$};
        \node[] (p3) at (3, -0.5) {\footnotesize$\mathcal{P}_{T_9} = \mathcal{P}_{T_6} = \mathcal{P}_{T_7}$};
        \begin{scope}[color=darkgray,dashed,line width=0.2ex]
        \path[->] (p1) edge[out=180, in=0] node[sloped,above] {} (pt1) ;
        \path[->] (p2) edge[out=180, in=60] node[sloped,above] {} (pt2) ;
        \path[->] (p3) edge[out=-90, in=30] node[sloped,above] {} (pt3) ;
        \end{scope}

        \node[anchor=south, yshift=0.1cm] at (b0.north) {\footnotesize$\langle \mathbf{c_{T_1}}, d(T_1) \rangle = \langle\mathbf{1}, 6\rangle$};
        \node[anchor=east,xshift=-0.1cm] at (b1.west) {\footnotesize$\langle \mathbf{1}, 5 \rangle$};
        \node[anchor=west,xshift=0.1cm] at (b2.east) {\footnotesize$\langle \mathbf{0}, 0 \rangle$};
        \node[anchor=east,xshift=-0.1cm] at (b3.west) {\footnotesize$\langle \mathbf{1}, 2 \rangle$};
        \node[anchor=west,xshift=0.1cm] at (b4.east) {\footnotesize$\langle \mathbf{1}, 3 \rangle$};
        \node[anchor=north west,xshift=0.1cm] at (b5.south east) {\footnotesize$\langle \mathbf{0}, 0 \rangle$};
        \node[anchor=north west] at (b6.south east) {\footnotesize$\langle \mathbf{0}, 0 \rangle$};
        \node[anchor=north west] at (b8.south east) {\footnotesize$\langle \mathbf{1}, 1 \rangle$};
        \node[anchor=north,yshift=-0.2cm] at (b7.south) {\footnotesize$\langle \mathbf{1}, 1 \rangle$};

    \end{scope}
\end{tikzpicture}

>>>>

\definecolor{lightgray}{HTML}{dddddd}
\definecolor{medgray}{HTML}{cccccc}
\definecolor{medgray2}{HTML}{bbbbbb}
\definecolor{darkgray}{HTML}{aaaaaa}
\definecolor{lightgp}{HTML}{ddddee}
\begin{tikzpicture}[x=1.12cm]
    \begin{scope}[all/.style={draw,fill=white,minimum height=0.5cm, minimum width=0.5cm},line width=0.08ex]
        \node[fill=lightgp, circle,minimum width=1cm] (pt1) at (0, 0) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt4) at (-1.5, -2) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt5) at (-0.5, -2) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt6) at (-2, -3) {};
        \fill[color=lightgp] plot[smooth cycle] coordinates { (1.2, -1) (0.9, -1.4) (-0.9, -1.4) (-1.2, -1) (-0.9, -0.6) (0.9, -0.6)} node (pt2) {};
        \fill[color=lightgp] plot[smooth cycle] coordinates {(2.1, -1.75) (2, -2.4) (0.6, -3.4) (0, -3.5) (-0.3, -3.3)(-0.3, -2.8) (0.1, -2.4) (1.2, -1.65) (1.7, -1.5) } node (pt3) {};
        \node[all, draw] (b0) at (0, 0) {$T_1$};
        \node[all, draw] (b1) at (-0.8, -1) {$T_2$};
        \node[all, draw] (b2) at (0.8, -1) {$T_3$};
        \node[all, draw] (b3) at (-1.5, -2) {$T_4$};
        \node[all, draw] (b4) at (-0.5, -2) {$T_5$};
        \node[all, draw] (b5) at (0.9, -2.5) {$T_6$};
        \node[all, draw] (b6) at (1.7, -2) {$T_7$};
        \node[all, draw] (b7) at (-2, -3) {$T_8$};
        \node[all, draw] (b8) at (0.2, -3) {$T_9$};
        \begin{scope}[line width=0.2ex]
        \path[->] (b1) edge[out=90, in=-110] node[sloped,above] {} (b0) ;
        \path[->] (b2) edge[out=100, in=-70] node[sloped,above] {} (b0) ;
        \path[->] (b3) edge[out=90, in=-110] node[sloped,above] {} (b1) ;
        \path[->] (b4) edge[out=90, in=-70] node[sloped,above] {} (b1) ;
        \path[->] (b5) edge[out=100, in=-110] node[sloped,above] {} (b2) ;
        \path[->] (b6) edge[out=120, in=-70] node[sloped,above] {} (b2) ;
        \path[->] (b7) edge[out=90, in=-90] node[sloped,above] {} (b3) ;
        \path[->] (b7) edge[out=0, in=-110] node[sloped,above] {} (b4) ;
        \path[->] (b8) edge[out=90, in=-70] node[sloped,above] {} (b4) ;
        \end{scope}
        \node[] (p1) at (3, 0.5) {\footnotesize$\mathcal{P}_{T_1}$};
        \node[] (p2) at (3, 0) {\footnotesize$\mathcal{P}_{T_2} = \mathcal{P}_{T_3}$};
        \node[] (p3) at (3, -0.5) {\footnotesize$\mathcal{P}_{T_9} = \mathcal{P}_{T_6} = \mathcal{P}_{T_7}$};
        \begin{scope}[color=darkgray,dashed,line width=0.2ex]
        \path[->] (p1) edge[out=180, in=0] node[sloped,above] {} (pt1) ;
        \path[->] (p2) edge[out=180, in=60] node[sloped,above] {} (pt2) ;
        \path[->] (p3) edge[out=-90, in=30] node[sloped,above] {} (pt3) ;
        \end{scope}
    \end{scope}
\end{tikzpicture}

### 2020-11-03 figures/dag.tex
add initial source and 'fr' make target

\definecolor{lightgray}{HTML}{dddddd}
\definecolor{medgray}{HTML}{cccccc}
\definecolor{medgray2}{HTML}{bbbbbb}
\definecolor{darkgray}{HTML}{aaaaaa}
\definecolor{lightgp}{HTML}{ddddee}
\begin{tikzpicture}[x=1.12cm, scale=0.9, every node/.append style={transform shape}]
    \begin{scope}[all/.style={draw, minimum height=0.5cm, minimum width=0.5cm},line width=0.08ex]
        \node[fill=lightgp, circle,minimum width=1cm] (pt1) at (0, 0) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt4) at (-1.5, -2) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt5) at (-0.5, -2) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt6) at (-2, -3) {};
        \fill[color=lightgp] plot[smooth cycle] coordinates { (1.2, -1) (0.9, -1.4) (-0.9, -1.4) (-1.2, -1) (-0.9, -0.6) (0.9, -0.6)} node (pt2) {};
        \fill[color=lightgp] plot[smooth cycle] coordinates {(2.1, -1.75) (2, -2.4) (0.6, -3.4) (0, -3.5) (-0.3, -3.3)(-0.3, -2.8) (0.1, -2.4) (1.2, -1.65) (1.7, -1.5) } node (pt3) {};
        \node[all, draw,fill=darkgray] (b0) at (0, 0) {$T_1$};
        \node[all, draw,fill=darkgray] (b1) at (-0.8, -1) {$T_2$};
        \node[all, draw,fill=white] (b2) at (0.8, -1) {$T_3$};
        \node[all, draw,fill=medgray] (b3) at (-1.5, -2) {$T_4$};
        \node[all, draw,fill=medgray2] (b4) at (-0.5, -2) {$T_5$};
        \node[all, draw,fill=white] (b5) at (0.9, -2.5) {$T_6$};
        \node[all, draw,fill=white] (b6) at (1.7, -2) {$T_7$};
        \node[all, draw,fill=lightgray] (b7) at (-2, -3) {$T_8$};
        \node[all, draw,fill=lightgray] (b8) at (0.2, -3) {$T_9$};
        \begin{scope}[line width=0.2ex]
        \path[->] (b1) edge[out=90, in=-110] node[sloped,above] {} (b0) ;
        \path[->] (b2) edge[out=100, in=-70] node[sloped,above] {} (b0) ;
        \path[->] (b3) edge[out=90, in=-110] node[sloped,above] {} (b1) ;
        \path[->] (b4) edge[out=90, in=-70] node[sloped,above] {} (b1) ;
        \path[->] (b5) edge[out=100, in=-110] node[sloped,above] {} (b2) ;
        \path[->] (b6) edge[out=120, in=-70] node[sloped,above] {} (b2) ;
        \path[->] (b7) edge[out=90, in=-90] node[sloped,above] {} (b3) ;
        \path[->] (b7) edge[out=0, in=-110] node[sloped,above] {} (b4) ;
        \path[->] (b8) edge[out=90, in=-70] node[sloped,above] {} (b4) ;
        \end{scope}
        \node[] (p1) at (3, 0.5) {\footnotesize$\mathcal{P}_{T_1}$} ;
        \node[] (p2) at (3, 0) {\footnotesize$\mathcal{P}_{T_2} = \mathcal{P}_{T_3}$};
        \node[] (p3) at (3, -0.5) {\footnotesize$\mathcal{P}_{T_9} = \mathcal{P}_{T_6} = \mathcal{P}_{T_7}$};
        \begin{scope}[color=darkgray,dashed,line width=0.2ex]
        \path[->] (p1) edge[out=180, in=0] node[sloped,above] {} (pt1) ;
        \path[->] (p2) edge[out=180, in=60] node[sloped,above] {} (pt2) ;
        \path[->] (p3) edge[out=-90, in=30] node[sloped,above] {} (pt3) ;
        \end{scope}

        \node[anchor=south, yshift=0.1cm] at (b0.north) {\footnotesize$\langle \mathbf{c_{T_1}}, d(T_1) \rangle = \langle\mathbf{1}, 6\rangle$};
        \node[anchor=east,xshift=-0.1cm] at (b1.west) {\footnotesize$\langle \mathbf{1}, 5 \rangle$};
        \node[anchor=west,xshift=0.1cm] at (b2.east) {\footnotesize$\langle \mathbf{0}, 0 \rangle$};
        \node[anchor=east,xshift=-0.1cm] at (b3.west) {\footnotesize$\langle \mathbf{1}, 2 \rangle$};
        \node[anchor=west,xshift=0.1cm] at (b4.east) {\footnotesize$\langle \mathbf{1}, 3 \rangle$};
        \node[anchor=north west,xshift=0.1cm] at (b5.south east) {\footnotesize$\langle \mathbf{0}, 0 \rangle$};
        \node[anchor=north west] at (b6.south east) {\footnotesize$\langle \mathbf{0}, 0 \rangle$};
        \node[anchor=north west] at (b8.south east) {\footnotesize$\langle \mathbf{1}, 1 \rangle$};
        \node[anchor=north,yshift=-0.2cm] at (b7.south) {\footnotesize$\langle \mathbf{1}, 1 \rangle$};

    \end{scope}
\end{tikzpicture}

>>>>

\definecolor{lightgray}{HTML}{dddddd}
\definecolor{medgray}{HTML}{cccccc}
\definecolor{medgray2}{HTML}{bbbbbb}
\definecolor{darkgray}{HTML}{aaaaaa}
\definecolor{lightgp}{HTML}{ddddee}
\begin{tikzpicture}[x=1.12cm]
    \begin{scope}[all/.style={draw, minimum height=0.5cm, minimum width=0.5cm},line width=0.08ex]
        \node[fill=lightgp, circle,minimum width=1cm] (pt1) at (0, 0) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt4) at (-1.5, -2) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt5) at (-0.5, -2) {};
        \node[fill=lightgp, circle,minimum width=1cm] (pt6) at (-2, -3) {};
        \fill[color=lightgp] plot[smooth cycle] coordinates { (1.2, -1) (0.9, -1.4) (-0.9, -1.4) (-1.2, -1) (-0.9, -0.6) (0.9, -0.6)} node (pt2) {};
        \fill[color=lightgp] plot[smooth cycle] coordinates {(2.1, -1.75) (2, -2.4) (0.6, -3.4) (0, -3.5) (-0.3, -3.3)(-0.3, -2.8) (0.1, -2.4) (1.2, -1.65) (1.7, -1.5) } node (pt3) {};
        \node[all, draw,fill=darkgray] (b0) at (0, 0) {$T_1$};
        \node[all, draw,fill=darkgray] (b1) at (-0.8, -1) {$T_2$};
        \node[all, draw,fill=white] (b2) at (0.8, -1) {$T_3$};
        \node[all, draw,fill=medgray] (b3) at (-1.5, -2) {$T_4$};
        \node[all, draw,fill=medgray2] (b4) at (-0.5, -2) {$T_5$};
        \node[all, draw,fill=white] (b5) at (0.9, -2.5) {$T_6$};
        \node[all, draw,fill=white] (b6) at (1.7, -2) {$T_7$};
        \node[all, draw,fill=lightgray] (b7) at (-2, -3) {$T_8$};
        \node[all, draw,fill=lightgray] (b8) at (0.2, -3) {$T_9$};
        \begin{scope}[line width=0.2ex]
        \path[->] (b1) edge[out=90, in=-110] node[sloped,above] {} (b0) ;
        \path[->] (b2) edge[out=100, in=-70] node[sloped,above] {} (b0) ;
        \path[->] (b3) edge[out=90, in=-110] node[sloped,above] {} (b1) ;
        \path[->] (b4) edge[out=90, in=-70] node[sloped,above] {} (b1) ;
        \path[->] (b5) edge[out=100, in=-110] node[sloped,above] {} (b2) ;
        \path[->] (b6) edge[out=120, in=-70] node[sloped,above] {} (b2) ;
        \path[->] (b7) edge[out=90, in=-90] node[sloped,above] {} (b3) ;
        \path[->] (b7) edge[out=0, in=-110] node[sloped,above] {} (b4) ;
        \path[->] (b8) edge[out=90, in=-70] node[sloped,above] {} (b4) ;
        \end{scope}
        \node[anchor=south, yshift=0.1cm] at (b0.north) {\footnotesize$(c, d) = (\textbf{1}, 5)$};
        \node[anchor=east,xshift=-0.1cm] at (b1.west) {\footnotesize$(\textbf{1}, 5)$};
        \node[anchor=west,xshift=0.1cm] at (b2.east) {\footnotesize$(\textbf{0}, 0)$};
        \node[anchor=east,xshift=-0.1cm] at (b3.west) {\footnotesize$(\textbf{1}, 2)$};
        \node[anchor=west,xshift=0.1cm] at (b4.east) {\footnotesize$(\textbf{1}, 3)$};
        \node[anchor=north west,xshift=0.1cm] at (b5.south east) {\footnotesize$(\textbf{0}, 0)$};
        \node[anchor=north west] at (b6.south east) {\footnotesize$(\textbf{0}, 0)$};
        \node[anchor=north west] at (b8.south east) {\footnotesize$(\textbf{1}, 1)$};
        \node[anchor=north,yshift=-0.2cm] at (b7.south) {\footnotesize$(\textbf{1}, 1)$};
        \node[] (p1) at (3, 0.5) {\footnotesize$\textrm{Parition 1}$};
        \node[] (p2) at (3, 0) {\footnotesize$\textrm{Parition 2}$};
        \node[] (p3) at (3, -0.5) {\footnotesize$\textrm{Parition 3}$};
        \node[] (p4) at (3, -1) {\footnotesize$\textrm{Parition 4}$};
        \node[] (p5) at (3, -1.5) {\footnotesize$\textrm{Parition 5}$};
        \node[] (p6) at (3, -2) {\footnotesize$\textrm{Parition 6}$};
        \begin{scope}[color=darkgray,dashed,line width=0.2ex]
        \path[->] (p1) edge[out=180, in=0] node[sloped,above] {} (pt1) ;
        \path[->] (p2) edge[out=180, in=60] node[sloped,above] {} (pt2) ;
        \path[->] (p3) edge[out=180, in=30] node[sloped,above] {} (pt3) ;
        \path[->] (p4) edge[out=170, in=30] node[sloped,above] {} (pt4) ;
        \path[->] (p5) edge[out=160, in=20] node[sloped,above] {} (pt5) ;
        \path[->] (p6) edge[out=270, in=-30] node[sloped,above] {} (pt6) ;
        \end{scope}
    \end{scope}
\end{tikzpicture}
